---
title: "Lab 10 Key"
author: "Taylor Gries"
date: "11/30/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(usethis)
library(janitor)

# New packages:
library(beepr)
library(praise)
library(cowsay)
library(paletteer)
library(sf)
```


# beepr beeps

Use the function `beep()` in the beepr package to make an audio alert when your code is done running.

```{r}
for (i in rev(seq(1:9999))) {
  
  print(paste(i, "bottles of beer on the wall"))
}

beep(4)
```


## praise and cowsay

Packages built with a singe purpose: to be kind and fun. 

```{r}
praise("${Exclamation},${EXCLAMATION}...${exclamation}!!!")

praise("Holy ${creating}, Batman - this code is ${ADJECTIVE}!")

praise("You are fucking ${adjective}!!")

say("hello world",
    by = "hypnotoad",
    what_color = c("royalblue1", "tomato2"),
    by_color = c("rainbow", "rainbow"))
```


Use cowsay::say() to make a character say something to you.

## Attach to github after the fact

usethis::use_git() 

usethis::use_github()

-do in the console since it is a onetime setup

-copy main code 

## paletteer to access thousands of color palettes

`View(palettes_d_names)` in console to see colors

```{r}
storms %>%
  group_by(name) %>%
  summarize(min_pressure = min(pressure, na.rm = TRUE)) %>%
  slice_min(n = 10, min_pressure) %>%
  ggplot(aes(x = min_pressure, y = name)) +
  geom_col(aes(fill = name)) +
  scale_fill_paletteer_d("beyonce::X120")
```

## One spatial data example

```{r}
vegetation <- read_sf("doc.kml") %>%
  select(Name) %>%
  clean_names()

ggplot(data = vegetation) +
  theme_minimal() +
  geom_sf(aes(fill = name), color = NA) +
  scale_fill_paletteer_d("khroma::land") + 
  labs(title = "Jornada Basin LTER Vegetation",
       caption = "Jornada LTER") 
```

```{r}
ggsave(filename = "jornada_basin_map_tg.jpg", width = 8, height = 5)
```




